Reproducibility and Open Science in Economics

### 2025-03-12 article.tex
More final final version

\author[1]{Lars Vilhuber}
\affil[1]{Cornell University}
\title{Reproducibility and Open Science in Economics}

@@

\maketitle

\section{Introduction}

@@

\begin{itemize}
\item open data: issues of data access, who can access, where to access, cost
\item open tools: is proprietary software a problem? what does the economics community dowell, what does it not do well? Stata is great, but costs money
\item persistence: while there are many solutions for relatively openly available data, what needs to be done for more restricted data (bring example from Swedish data archive, Goncalves case)
\item collaborative methods: long history of sharing working papers, rarely any issue with sharing code. Possible coding errors may inhibit stronger" standing on others shoulders
\end{itemize}

>>>>

\newtoggle{anonymous}
\newtoggle{draft}
%\settoggle{anonymous}{true}
\settoggle{anonymous}{false}
\settoggle{draft}{false}

\iftoggle{anonymous}{\author{Anonymous}}{
\author[1]{Lars Vilhuber}
\affil[1]{Cornell University}
}
\title{Reproducibility and Open Science in Economics}

@@

\maketitle
\input{abstract}
\newpage
\section{Introduction}

@@

% \begin{itemize}
% \item open data: issues of data access, who can access, where to access, cost
% \item open tools: is proprietary software a problem? what does the economics community dowell, what does it not do well? Stata is great, but costs money
% \item persistence: while there are many solutions for relatively openly available data, what needs to be done for more restricted data (bring example from Swedish data archive, Goncalves case)
% \item collaborative methods: long history of sharing working papers, rarely any issue with sharing code. Possible coding errors may inhibit stronger" standing on others shoulders
% \end{itemize}
